### 2022-01-09 abstract.tex
extend abstract

    In this work, we present a novel, completely software-based approach to this challenge.
    Our core idea rests on a \emph{hardware-in-the-loop} approach in which we emulate a physical plant which communicates over a real network with a controller implemented in software.
    Our approach is furthermore designed and built for the Edge, using a general-purpose programming language and will full compatibility with industry-standard containerization solutions.
\end{abstract}

>>>>

    In this work, we present a novel, completely software-based approach to this challenge.
    Our core idea rests on a \emph{hardware-in-the-loop} approach in which we emulate a physical plant which communicates over a real network with a controller implemented in software.
    This approach is furthermore designed and built for the Edge, using a general-purpose programming language and will full compatibility with industry-standard containerization solutions.
    Our results showcase the utility of this framework as a repeatable and scalable solution to \ac{NCS} performance evaluation.
\end{abstract}
